---
output: pdf_document
geometry: margin=1in
mainfont: Times New Roman
---

```{r s1,warning=F, message=F, echo=F,comment="K",results='hide'}
#load all datasets

library(repmis)
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS1_dosedata.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS2_allRIAILregressed.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS3_allRIAILsPC.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS4_allAnnotatedLods.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS5_scantwosummary.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS6_varianceComponents.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS9_allNILCSSregressed.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS10_css_nil_stats.Rda?raw=TRUE")
source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS11_assays_category.Rda?raw=TRUE")
library(linkagemapping)
data("N2xCB4856cross")

```


```{r s1_2,warning=F, message=F, echo=F,comment="K",results='asis'}
library(pander)
library(stringr)
library(knitr)
library(scales)
library(cowplot)
library(tidyverse)
library(reshape2)
library(repmis)

panderOptions('knitr.auto.asis', TRUE)

cat("\n\n\n")
cat("\n\n\\pagebreak\n")
    
#Load Data
#source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS1_dosedata.Rda?raw=TRUE")

#### Dose response
dosedrugs <- c("cadmium", "carmustine", "chlorothalonil", "chlorpyrifos", "cisplatin", "copper", "diquat", "fluoxetine", "FUdR", "irinotecan", "mechlorethamine", "paraquat", "silver", "topotecan", "tunicamycin", "vincristine")

dosecontrols <- c("water", "DMSO", "DMSO", "DMSO", "water", "water", "water", "DMSO", "water" ,"DMSO", "water", "water", "water", "water", "DMSO", "water")

doseplates <- c(23, 5, 6, 22, 3, 4, 2, 11, 9, 12, 1, 7, 21, 15, 17, 8)

cadmiumconc <- factor(c("water", "cadmium100", "cadmium200", "cadmium300", "cadmium400"), levels = c("water", "cadmium100", "cadmium200", "cadmium300", "cadmium400"))
carmustineconc <- factor(c("DMSO", "carmustine125", "carmustine250", "carmustine500","carmustine1000"), levels = c("DMSO", "carmustine125", "carmustine250", "carmustine500","carmustine1000"))
chlorothalonilconc <- factor(c("DMSO","chlorothalonil125","chlorothalonil250","chlorothalonil500","chlorothalonil1000"), levels = c("DMSO","chlorothalonil125","chlorothalonil250","chlorothalonil500","chlorothalonil1000"))
chlorpyrifosconc <- factor(c("DMSO","chlorpyrifos025","chlorpyrifos05","chlorpyrifos1","chlorpyrifos2"), levels =c("DMSO","chlorpyrifos025","chlorpyrifos05","chlorpyrifos1","chlorpyrifos2"))
cisplatinconc <- factor(c("water","cisplatin125","cisplatin250","cisplatin500","cisplatin1000"), levels = c("water","cisplatin125","cisplatin250","cisplatin500","cisplatin1000"))
copperconc <- factor(c("water","copper625","copper125","copper250","copper500"), levels = c("water","copper625","copper125","copper250","copper500"))
diquatconc <- factor(c("water","diquat250","diquat500","diquat1000","diquat2000"), levels = c("water","diquat250","diquat500","diquat1000","diquat2000"))
fluoxetineconc <- factor(c("DMSO","fluoxetine625","fluoxetine125","fluoxetine250","fluoxetine500"), levels = c("DMSO","fluoxetine625","fluoxetine125","fluoxetine250","fluoxetine500"))
fudrconc <- factor(c("water", "FUdR375", "FUdR50", "FUdR75", "FUdR100"), levels = c("water", "FUdR375", "FUdR50", "FUdR75", "FUdR100"))
irinotecanconc <- factor(c("DMSO","irinotecan625","irinotecan125","irinotecan250","irinotecan500"), levels = c("DMSO","irinotecan625","irinotecan125","irinotecan250","irinotecan500"))
mechlorethamineconc <- factor(c("water","mechlorethamine200","mechlorethamine300","mechlorethamine400","mechlorethamine500"), levels = c("water","mechlorethamine200","mechlorethamine300","mechlorethamine400","mechlorethamine500"))
paraquatconc <- factor(c("water","paraquat500","paraquat1000","paraquat2000","paraquat4000"), levels = c("water","paraquat500","paraquat1000","paraquat2000","paraquat4000"))
silverconc <- factor(c("water","silver75","silver150","silver300","silver500"), levels = c("water","silver75","silver150","silver300","silver500"))
topotecanconc <- factor(c("water","topotecan50","topotecan100","topotecan200","topotecan400"), levels = c("water","topotecan50","topotecan100","topotecan200","topotecan400"))
tunicamycinconc <- factor(c("DMSO","tunicamycin5","tunicamycin10","tunicamycin15","tunicamycin20"), levels = c("DMSO","tunicamycin5","tunicamycin10","tunicamycin15","tunicamycin20"))
vincristineconc <- factor(c("water","vincristine20","vincristine40","vincristine60","vincristine80"), levels = c("water","vincristine20","vincristine40","vincristine60","vincristine80"))


concentrations <- list(cadmiumconc, carmustineconc, chlorothalonilconc, chlorpyrifosconc, cisplatinconc, copperconc, diquatconc, fluoxetineconc, fudrconc, irinotecanconc, mechlorethamineconc, paraquatconc, silverconc, topotecanconc, tunicamycinconc, vincristineconc)

cadmiumlabs <- c("0", "100","200","300","400")
carmustinelabs <- c("0", "125", "250", "500", "1000")
chlorothalonillabs <- c("0", "125", "250", "500", "1000")
chlorpyrifoslabs <- c("0",".25",".5","1","2")
cisplatinlabs <- c("0","125","250","500","1000")
copperlabs <- c("0","62.5","125","250","500")
diquatlabs <- c("0","250","500","1000","2000")
fluoxetinelabs <- c("0","62.5","125","250","500")
fudrlabs <- c("0", "37.5", "50", "75", "100")
irinotecanlabs <- c("0","62.5","125","250","500")
mechlorethaminelabs <- c("0","200","300","400","500")
paraquatlabs <- c("0","500","1000","2000","4000")
silverlabs <- c("0","75","150","300","500")
topotecanlabs <- c("0","50","100","200","400")
tunicamycinlabs <- c("0","5","10","15","20")
vincristinelabs <- c("0","20","40","60","80")

doselabels <- list(cadmiumlabs, carmustinelabs, chlorothalonillabs, chlorpyrifoslabs, cisplatinlabs, copperlabs, diquatlabs, fluoxetinelabs, fudrlabs, irinotecanlabs, mechlorethaminelabs, paraquatlabs, silverlabs, topotecanlabs, tunicamycinlabs, vincristinelabs)

##### Trait correlation
traitcordrugs <- dosedata %>%
  dplyr::filter(condition %in% c("cadmium100", "carmustine250","chlorothalonil250","chlorpyrifos1","cisplatin250","copper250","diquat250","fluoxetine250","FUdR50","irinotecan125","mechlorethamine200","paraquat500","silver150","topotecan400","tunicamycin10","vincristine80"))

traitcordrugs$condition <- factor(traitcordrugs$condition, levels = c("cadmium100", "carmustine250","chlorothalonil250","chlorpyrifos1","cisplatin250","copper250","diquat250","fluoxetine250","FUdR50","irinotecan125","mechlorethamine200","paraquat500","silver150","topotecan400","tunicamycin10","vincristine80"), labels = c("Cadmium 100 µM", "Carmustine 250 µM","Chlorothalonil 250 µM","Chlorpyrifos 1 µM","Cisplatin 250 µM","Copper 250 µM","Diquat 250 µM","Fluoxetine 250 µM","FUdR 50 µM","Irinotecan 125 µM","Mechlorethamine 200 µM","Paraquat 500 µM","Silver 150 µM","Topotecan 400 µM","Tunicamycin 10 µM","Vincristine 80 µM"))

splitbydose <- split(traitcordrugs, paste(traitcordrugs$condition))

```

```{r s1_3, fig.width=7.5, fig.height=10,warning=F, message=F, echo=F,comment="K",results='asis', dpi = 300}

  reorder_cormat <- function(cormat){
  # Use correlation between variables as distance
  dd <- as.dist((1-cormat)/2)
  hc <- hclust(dd)
  cormat <-cormat[hc$order, hc$order]
}

for (i in 1:length(dosedrugs)) {
        
        traitdf <- dosedata %>%
            dplyr::filter(trait %in% c("norm.n", "mean.TOF","mean.norm.EXT"), grepl(dosedrugs[i], condition)|grepl(dosecontrols[i],condition), plate == doseplates[i]) %>%
            dplyr::group_by(strain)
        
        traitdf$trait <- factor(traitdf$trait, levels = c("norm.n","mean.TOF","mean.norm.EXT"), labels = c("Brood Size", "Mean Length", "Mean Optical Density"))
        
        doseplot <- ggplot2::ggplot(traitdf) +
          ggplot2::theme_bw()+
          ggplot2::aes(x=condition, y=phenotype, fill=strain) +
          ggplot2::geom_point(position = position_jitterdodge(jitter.width = 0.2), size = .5)+
          ggplot2::geom_boxplot(outlier.size=NA, outlier.color = NA,alpha = .5)+
          ggplot2::scale_x_discrete(limits=levels(concentrations[[i]]), labels = doselabels[[i]])+
          ggplot2::scale_fill_manual(values=c("blue","green","pink","orange"), guide_legend(title = "Strain"))+
          ggplot2::ggtitle(Hmisc::capitalize(dosedrugs[i])) +
          ggplot2::labs(x = "Concentration (µM)", y = "Raw Phenotype") +
          ggplot2::facet_wrap(~ trait, scales = "free") +
          ggplot2::theme(axis.text.x = ggplot2::element_text(size=10, face = "bold", color="black"),
                         axis.text.y = ggplot2::element_text(size=10, face = "bold", color="black"),
                         axis.title.x = ggplot2::element_text(size=12, face = "bold", color="black"),
                         axis.title.y = ggplot2::element_text(size=12, face = "bold", color="black"),
                         plot.title = ggplot2::element_text(size=12, face = "bold", color = "black", hjust = .5),
                         strip.background = ggplot2::element_rect(fill = NA),
                         strip.text = ggplot2::element_text(size = 12, face = "bold", color = "black"),
                         legend.text = ggplot2::element_text(size = 10, face = "bold", color = "black"),
                         legend.title = ggplot2::element_text(size = 10, face = "bold", color = "black"),
                         legend.key.size = grid::unit(.2, "in"),
                         legend.margin = ggplot2::margin(0, 0, 0, 0, "in"))

            traitcor <- splitbydose[[i]] %>%
              dplyr::filter(trait %in% c("n","norm.n", "q10.TOF", "q10.EXT", "q25.TOF", "q25.EXT", "median.TOF", "median.EXT", "mean.TOF", "mean.EXT", "q75.TOF",
                                         "q75.EXT", "q90.TOF", "q90.EXT", "var.TOF", "var.EXT", "cv.TOF", "cv.EXT", "q10.norm.EXT", "q25.norm.EXT", "median.norm.EXT", "mean.norm.EXT",
                                         "q75.norm.EXT", "q90.norm.EXT"))
  #ordered traits based on correlation structure for each toxin:
            # traitcor$trait <- factor(traitcor$trait, levels = c("n","norm.n", "q10.TOF", "q10.EXT", "q25.TOF", "q25.EXT", "median.TOF", "median.EXT", "mean.TOF",
            #                                                     "mean.EXT", "q75.TOF", "q75.EXT", "q90.TOF", "q90.EXT", "var.TOF", "var.EXT", "cv.TOF", "cv.EXT", "q10.norm.EXT",
            #                                                     "q25.norm.EXT", "median.norm.EXT", "mean.norm.EXT", "q75.norm.EXT", "q90.norm.EXT"))
  
  
            traitcor<- traitcor %>%
              tidyr::spread(trait, phenotype) %>%
              dplyr::ungroup() %>%
              dplyr::select(cv.EXT:var.TOF)
            traitcormat <- cor(traitcor)
            reordered <- reorder_cormat(traitcormat)
            
            save_plot <- ggplot2::ggplot(data=melt(reordered), ggplot2::aes(Var1,Var2, fill=value^2))+
              ggplot2::geom_tile() +
              ggplot2::scale_fill_gradientn(colours=terrain.colors(6), name=expression(bold(italic("r")^2)))+
              ggplot2::theme_bw() +
              ggplot2::theme(axis.text.x = ggplot2::element_text(size=10, face = "bold", color="black", angle=60, hjust=1),
                    axis.text.y = ggplot2::element_text(size=10, face = "bold", color="black"),
                    plot.title = ggplot2::element_text(size = 12, face = "bold", color = "black", hjust = .5),
                    panel.background = ggplot2::element_rect(fill = '#E5E8E8'),
                    legend.text = ggplot2::element_text(size = 10, face = "bold", color = "black"),
                    legend.title = ggplot2::element_text(size = 10, face = "bold", color = "black"))+
              ggplot2::labs(title=splitbydose[[i]]$condition[1], x=NULL, y=NULL)
            
          print(cowplot::plot_grid(doseplot, save_plot, nrow = 2, ncol = 1, labels = c("A", "B"), rel_heights = c(1, 2)))

          cat("\n\n\n")
          cat("\n\n\\pagebreak\n")
        
}
```

**Figure S1** Dose-response and trait correlation estimates. (**A**) Raw phenotypic values for four divergent strains, CB4856 (blue), DL238 (green), JU258 (pink), and N2 (orange), in response to various concentrations of each toxin are plotted as Tukey box plots. Toxin responses for traits representing three distinct population parameters- brood size (norm.n), mean animal length (mean.TOF), and mean optical density (mean.norm.EXT) are shown. The x-axis indicates either the control (water or DMSO) or the concentration (µM) of the toxin, and the y-axis shows the raw phenotypic value for each trait. (**B**) Correlation coefficients (r^2^) between all pairwise combinations of traits for the indicated concentration of the toxin are plotted as a heat map. Traits are labeled on the x- and y-axes, organized by heirarchical clustering of the correlation matrix for each toxin. Colors represent correlation coefficients increasing from green to yellow to pink to white.


```{r s2,warning=F, message=F, echo=F,comment="K",results='asis'}
library(pander)
library(stringr)
library(knitr)
library(scales)
library(cowplot)
library(tidyverse)
library(reshape2)
library(linkagemapping)

panderOptions('knitr.auto.asis', TRUE)

cat("\n\n\n")
cat("\n\n\\pagebreak\n")
# 
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS2_allRIAILregressed.Rda?raw=TRUE")
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS3_allAnnotatedLods.Rda?raw=TRUE")
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS9_allNILCSSregressed.Rda?raw=TRUE")
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS10_css_nil_stats.Rda?raw=TRUE")
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS5_varianceComponents.Rda?raw=TRUE")
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS11_assays_category.Rda?raw=TRUE")
# 
# data("N2xCB4856cross")

#Make the cross object
phenocross <- linkagemapping::mergepheno(N2xCB4856cross, allRIAILregressed, set = 2)

#VE_SE_QTL
VE <- varianceComponents %>%
  dplyr::select(condition, trait, narrowsense_h2, interaction_VE) %>%
  tidyr::gather(type, VE, narrowsense_h2:interaction_VE) %>%
  dplyr::mutate(type = ifelse(type == "narrowsense_h2", "Additive", "Interactive"))

SE <- varianceComponents %>%
  dplyr::select(condition, trait, narrowsense_h2_SE, interaction_SE) %>%
  tidyr::gather(type, SE, narrowsense_h2_SE:interaction_SE) %>%
  dplyr::mutate(type = ifelse(type == "narrowsense_h2_SE", "Additive", "Interactive"))

VE_SE_QTL <- dplyr::left_join(VE, SE) %>%
  dplyr::mutate(n = 1:nrow(.))

VE_SE_QTL$type <- factor(VE_SE_QTL$type, levels = c("Interactive", "Additive"))
VE_SE_QTL <- VE_SE_QTL %>%
  dplyr::mutate(lower = VE - SE, higher = VE + SE)

VE_SE_QTL$lower[VE_SE_QTL$type == "Interactive"] <- with(VE_SE_QTL,VE[type == "Additive"] - SE[type == "Interactive"] + VE[type == "Interactive"])
VE_SE_QTL$higher[VE_SE_QTL$type == "Interactive"] <- with(VE_SE_QTL,VE[type == "Interactive"] + VE[type == "Additive"] + SE[type == "Interactive"])

for(i in 1:nrow(VE_SE_QTL)) {
  if(VE_SE_QTL$lower[i] < 0) {
    VE_SE_QTL$lower[i] <- 0
  }
}

#Separate NIL phenotype data by experiment
chrVregressed <- allNILCSSregressed %>%
  dplyr::filter(experiment == "V")
chrIVLregressed <- allNILCSSregressed %>%
  dplyr::filter(experiment == "IVL")
chrIVRregressed <- allNILCSSregressed %>%
  dplyr::filter(experiment == "IVR")
cssVregressed <- allNILCSSregressed %>%
  dplyr::filter(experiment == "CSSV")


#Load functions
#Define function for NIL mapping
x1 <- .25
y1 <- .02
y2 <- 0.01
blck <- .12
spce <- .06
x2 <- x1+blck+spce
x3 <- x2+blck+spce
x4 <- x3+blck+spce
width <- .02
chr <- 0.02
textsize = 8
titlesize = 10
pointsize = 0.3

#Define function for NIL mapping
quick_plot_V <- function(cond, pltrt, signif, ylab = pltrt, t = "NIL"){
  phen_gen <- allNILCSSregressed %>%
    dplyr::filter(experiment == "V", trait == pltrt, condition == cond)
  
  if(is.null(signif)) {
    phen_gen$strain <- factor(phen_gen$strain, levels = unique(phen_gen$strain), ordered = T)
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = strain, y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA230" = "gray", "ECA232" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
                     axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
                     axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
                     axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     legend.position="none",
                     plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
                     panel.background = ggplot2::element_rect(color="black",size=1),
                     strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      ggplot2::labs(y= ylab, x = "", title = t) 
  } else {
    phen_gen$strain <- factor(phen_gen$strain, levels = unique(phen_gen$strain), ordered = T)
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = strain, y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA230" = "gray", "ECA232" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_text(data = signif, ggplot2::aes(x = strain, y = pheno, label = significant), size = 3, color = "black", fontface = "bold") +
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
                     axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
                     axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
                     axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     legend.position="none",
                     plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
                     panel.background = ggplot2::element_rect(color="black",size=1),
                     strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      #ggplot2::ylim(NA, max(phen_gen$phenotype)*1.7)+
      ggplot2::labs(y= ylab, x = "", title = t) 
  }
  
  cowplot::ggdraw() +
    cowplot::draw_plot(test, 0, .03, 1, .97) +
    cowplot::draw_label("Chr V", x = 0.01, y = .08, size = textsize, fontface = "bold", hjust = -.16)+
    ggplot2::geom_rect(ggplot2::aes(xmin = x1+chr, xmax = x1+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x2+chr, xmax = x2+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+chr, xmax = x3+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+blck*.25+chr, xmax = x3+blck*.75-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4+chr, xmax = x4+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4+blck*.25+chr, xmax = x4+blck*.75-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+
    cowplot::draw_label("Genome", x = 0.01, y = .05, hjust = -.1, size = textsize, fontface = "bold") +
    ggplot2::geom_rect(ggplot2::aes(xmin = x1, xmax = x1+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x2, xmax = x2+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3, xmax = x3+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4, xmax = x4+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "orange")
}
quick_plot_IVR <- function(cond, pltrt, signif, ylab = pltrt, t = "NIL"){
  phen_gen <- allNILCSSregressed %>%
    dplyr::filter(experiment == "IVR", trait == pltrt, condition == cond)
  
  if(is.null(signif)) {
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = factor(strain, levels = c("N2", "CB4856", "ECA241", "ECA240"), 
                              labels = c("N2", "CB4856", "ECA241", "ECA240"), ordered = T),
                   y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA241" = "gray", "ECA240" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
                     axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
                     axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
                     axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     legend.position="none",
                     plot.margin = ggplot2::margin(t = 0, r = 10, b = 30, l = 0),
                     plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
                     panel.background = ggplot2::element_rect(color="black",size=1),
                     strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      ggplot2::labs(y= ylab, x = "", title = t) 
  } else{
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = factor(strain, levels = c("N2", "CB4856", "ECA241", "ECA240"),
                              labels = c("N2", "CB4856", "ECA241", "ECA240"), ordered = T),
                   y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA241" = "gray", "ECA240" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_text(data = signif, ggplot2::aes(x = strain, y = pheno, label = significant), 
                         size = 3, color = "black", fontface = "bold") +
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      # coord_flip() +
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
                     axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
                     axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
                     axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     legend.position="none",
                     panel.background = ggplot2::element_rect(color="black",size=1),
                     plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
                     strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      # ggplot2::ylim(NA, max(phen_gen$phenotype)*1.5)+
      ggplot2::labs(y= ylab, x = "", title = t) 
  }
  
  cowplot::ggdraw() +
    cowplot::draw_plot(test, 0, .03, 1, .97) +
    cowplot::draw_label("Chr IV", x = 0.01, y = .08, size = textsize, fontface = "bold", hjust = -.16)+
    ggplot2::geom_rect(ggplot2::aes(xmin = x1+chr, xmax = x1+blck-chr, ymin = y1*3, ymax = y1*3 + width),
                       colour = "black", fill = "orange")+ #N2 chr
    ggplot2::geom_rect(ggplot2::aes(xmin = x2+chr, xmax = x2+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+ #CB chr
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+chr, xmax = x3+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+ #First NIL chr
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+blck*.5+chr, xmax = x3+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+ #first NIL introgressed
    ggplot2:: geom_rect(ggplot2::aes(xmin = x4+chr, xmax = x4+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                        colour = "black", fill = "orange")+ #Last NIL chr
    ggplot2::geom_rect(ggplot2::aes(xmin = x4+blck*.5+chr, xmax = x4+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+ #Last NIL introgressed
    cowplot::draw_label("Genome", x = 0.01, y = .05, hjust = -.1, size = textsize, fontface = "bold") +
    ggplot2::geom_rect(ggplot2::aes(xmin = x1, xmax = x1+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "orange")+ #N2 genome
    ggplot2::geom_rect(ggplot2::aes(xmin = x2, xmax = x2+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "blue")+ #CB genome
    ggplot2::geom_rect(ggplot2::aes(xmin = x3, xmax = x3+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "blue")+ #First NIL genome
    ggplot2::geom_rect(ggplot2::aes(xmin = x4, xmax = x4+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "orange") #last NIL genome
}
quick_plot_cssV <- function(cond, pltrt, signif, ylab = pltrt, t = "CSS"){
  phen_gen <- allNILCSSregressed %>%
    dplyr::filter(experiment == "CSSV", trait == pltrt, condition == cond)
  
  if(is.null(signif)) {
    phen_gen$strain <- factor(phen_gen$strain, levels = unique(phen_gen$strain), ordered = T)
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = strain, y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA554" = "gray", "ECA573" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
            axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
            axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
            axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
            strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
            legend.position="none",
            plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
            panel.background = ggplot2::element_rect(color="black",size=1),
            strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      ggplot2::labs(y= ylab, x = "", title = t) 
  } else {
    phen_gen$strain <- factor(phen_gen$strain, levels = unique(phen_gen$strain), ordered = T)
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = strain, y = phenotype, fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA554" = "gray", "ECA573" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_text(data = signif, ggplot2::aes(x = strain, y = pheno, label = significant), size = 3, color = "black", fontface = "bold") +
      ggplot2::geom_boxplot(outlier.colour = NA, aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
            axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
            axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
            axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
            strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
            plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
            legend.position="none",
            panel.background = ggplot2::element_rect(color="black",size=1),
            strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      # ggplot2::ylim(NA, max(phen_gen$phenotype)*1.5)+
      ggplot2::labs(y= ylab, x = "", title = t) 
  }
  
  cowplot::ggdraw() +
    cowplot::draw_plot(test, 0, .03, 1, .97) +
    cowplot::draw_label("Chr V", x = 0.01, y = .08, size = textsize, fontface = "bold", hjust = -.16)+
    ggplot2::geom_rect(ggplot2::aes(xmin = x1+chr, xmax = x1+blck-chr, ymin = y1*3, ymax = y1*3 +width),
              colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x2+chr, xmax = x2+blck-chr, ymin = y1*3, ymax = y1*3 +width),
              colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+chr, xmax = x3+blck-chr, ymin = y1*3, ymax = y1*3 +width),
              colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4+chr, xmax = x4+blck-chr, ymin = y1*3, ymax = y1*3 +width),
              colour = "black", fill = "blue")+
    cowplot::draw_label("Genome", x = 0.01, y = .05, hjust = -.1, size = textsize, fontface = "bold") +
    ggplot2::geom_rect(ggplot2::aes(xmin = x1, xmax = x1+blck, ymin = y2*3, ymax = y2*3 +width),
              colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x2, xmax = x2+blck, ymin = y2*3, ymax = y2*3 +width),
              colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3, xmax = x3+blck, ymin = y2*3, ymax = y2*3 +width),
              colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4, xmax = x4+blck, ymin = y2*3, ymax = y2*3 +width),
              colour = "black", fill = "orange")
}
quick_plot_IVL <- function(cond, pltrt, signif, ylab = pltrt, t = "NIL"){
  phen_gen <- allNILCSSregressed %>%
    dplyr::filter(experiment == "IVL", trait == pltrt, condition == cond)
  
  if(is.null(signif)) {
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = factor(strain, levels = c("N2", "CB4856", "ECA229", "ECA231"), 
                              labels = c("N2", "CB4856", "ECA229", "ECA231"), ordered = T), 
                   y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA229" = "gray", "ECA231" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
                     axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
                     axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
                     axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     legend.position="none",
                     plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
                     panel.background = ggplot2::element_rect(color="black",size=1),
                     strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      ggplot2::labs(y= ylab, x = "", title = t) 
  } else {
    test <- phen_gen %>%
      ggplot2::ggplot(.)+
      ggplot2::aes(x = factor(strain, levels = c("N2", "CB4856", "ECA229", "ECA231"), 
                              labels = c("N2", "CB4856", "ECA229", "ECA231"), ordered = T), 
                   y = phenotype,fill=strain)+
      ggplot2::scale_fill_manual(values = c("N2" = "orange", "CB4856"= "blue", "ECA229" = "gray", "ECA231" = "gray"))+
      ggplot2::geom_jitter(alpha = 1, size = pointsize)+
      ggplot2::geom_text(data = signif, ggplot2::aes(x = strain, y = pheno, label = significant), size = 3, color = "black", fontface = "bold") +
      ggplot2::geom_boxplot(outlier.colour = NA, ggplot2::aes(alpha = 0.8))+
      ggplot2::theme_bw()+
      ggplot2::theme(axis.text.x = ggplot2::element_text(size=textsize, face="bold", color="black"),
                     axis.text.y = ggplot2::element_text(size=textsize,  face = "bold", color="black"),
                     axis.title.x = ggplot2::element_text(size=titlesize, color="black", vjust=-.3, face = "bold"),
                     axis.title.y = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     strip.text = ggplot2::element_text(size=titlesize,  color="black", face = "bold"),
                     legend.position="none",
                     plot.title = ggplot2::element_text(size=titlesize, color = "black", face = "bold", hjust = 0.5),
                     panel.background = ggplot2::element_rect(color="black",size=1),
                     strip.background = ggplot2::element_rect(color = "black", size = 1)) + 
      # ggplot2::ylim(NA, max(phen_gen$phenotype)*1.5)+
      ggplot2::labs(y= ylab, x = "", title = t) 
  }
  
  cowplot::ggdraw() +
    cowplot::draw_plot(test, 0, .03, 1, .97) +
    cowplot::draw_label("Chr IV", x = 0.01, y = .08, size = textsize, fontface = "bold", hjust = -.16)+
    ggplot2::geom_rect(ggplot2::aes(xmin = x1+chr, xmax = x1+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x2+chr, xmax = x2+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+chr, xmax = x3+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3+blck*.25+chr, xmax = x3+blck*.75-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4+chr, xmax = x4+blck-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4+blck*.25+chr, xmax = x4+blck*.75-chr, ymin = y1*3, ymax = y1*3 +width),
                       colour = "black", fill = "blue")+
    cowplot::draw_label("Genome", x = 0.01, y = .05, hjust = -.1, size = textsize, fontface = "bold") +
    ggplot2::geom_rect(ggplot2::aes(xmin = x1, xmax = x1+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "orange")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x2, xmax = x2+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x3, xmax = x3+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "blue")+
    ggplot2::geom_rect(ggplot2::aes(xmin = x4, xmax = x4+blck, ymin = y2*3, ymax = y2*3 +width),
                       colour = "black", fill = "orange")
}

# More functions for plotting
maxlodplot_kt <- function (map) {
  map1 <- map %>% 
    dplyr::group_by(marker) %>% 
    dplyr::filter(lod ==max(lod))
  tit <- paste0(unique(map$condition), ".", unique(map$trait))
  cis <- map %>% 
    dplyr::group_by(marker) %>% 
    dplyr::mutate(maxlod = max(lod)) %>%
    dplyr::group_by(iteration) %>% 
    dplyr::filter(!is.na(var_exp)) %>%
    dplyr::do(head(., n = 1))
  if (nrow(cis) == 0) {
    plot <- ggplot2::ggplot(map1, ggplot2::aes(x = genotype,y = pheno)) + 
      ggplot2::geom_blank()
    return(plot)
  }
  map1 <- linkagemapping:::cidefiner(cis, map1)
  plot <- ggplot2::ggplot(map1) + ggplot2::aes(x = pos/1e+06,y = lod)
  if (nrow(cis) != 0) {
    plot <- plot + 
      ggplot2::geom_ribbon(ggplot2::aes(x = pos/1e+06,ymin = 0, ymax = ci_lod), fill = "blue", alpha = 0.5) +
      ggplot2::geom_point(data = cis, ggplot2::aes(x = pos/1e+06,y = (1.05 * maxlod)), fill = "red", shape = 25,
                          size = 3.2, show.legend = FALSE) + 
      ggplot2::ylim(0, 1.5*max(cis$maxlod))+
      ggplot2::geom_text(data = cis, ggplot2::aes(x = pos/1e+06, y = (1.2 * maxlod), label = paste0(100 *round(var_exp, digits = 4), "%")), colour = "black",size = 3, hjust = "inward")
  }
  
  plot <- plot + 
    ggplot2::geom_line(size = 0.75, alpha = 0.85) +
    ggplot2::facet_grid(. ~ chr, scales = "free", space = "free") +
    ggplot2::labs(x = "Genomic Position (Mb)", y = "LOD") +
    ggplot2::scale_colour_discrete(name = "Mapping\nIteration") +
    ggplot2::ggtitle(map1$trait[1]) + 
    ggplot2::theme_bw() +
    ggplot2::theme(
      axis.text.x = ggplot2::element_text(size = textsize, color = "black", face = "bold"),
      axis.text.y = ggplot2::element_text(size = textsize, color = "black", face = "bold"),
      axis.title.x = ggplot2::element_text(size = titlesize, color="black", face = "bold"),
      axis.title.y = ggplot2::element_text(size = titlesize,color="black", face = "bold"),
      strip.text.x = ggplot2::element_text(size = titlesize, color = "black"),
      strip.text.y = ggplot2::element_text(size = titlesize, color = "black"),
      strip.background = ggplot2::element_rect(colour = "black", fill = "white", size = 0.75, linetype = "solid"),
      plot.title = ggplot2::element_text(size = (titlesize+5),color="black", face = "bold"),
      panel.background = ggplot2::element_rect(color = "black", size = 1.2)) + 
    ggplot2::labs(title = tit)
  return(plot)
}
pxgplot_kt <- function (cross, map, parent = "N2xCB4856", tit = "", ylab = "") {
  peaks <- map %>% 
    dplyr::group_by(iteration) %>% 
    dplyr::filter(!is.na(var_exp)) %>% 
    dplyr::do(head(., n = 1))
  
  if (nrow(peaks) == 0) {
    stop("No QTL identified")
  }
  uniquemarkers <- gsub("-", "\\.", unique(peaks$marker))
  colnames(cross$pheno) <- gsub("-", "\\.", colnames(cross$pheno))
  pheno <- cross$pheno %>% 
    dplyr::select_(map$trait[1])
  geno <- data.frame(linkagemapping:::extract_genotype(cross)) %>% 
    dplyr::select(which(colnames(.) %in% uniquemarkers)) %>% 
    data.frame(., pheno)
  colnames(geno)[1:(ncol(geno) - 1)] <- sapply(colnames(geno)[1:(ncol(geno) - 1)], 
                                               function(marker) {paste(unlist(peaks[peaks$marker == gsub("\\.", "-", marker),
                                                                                    c("chr", "pos")]), collapse = ":")})
  colnames(geno)[ncol(geno)] <- "pheno"
  split <- tidyr::gather(geno, marker, genotype, -pheno)
  split$genotype <- sapply(split$genotype, function(x) {
    if (is.na(x)) {
      return(NA)
    }
    if (parent == "N2xCB4856") {
      if (x == -1) {
        "N2"
      }
      else {
        "CB4856"
      }
    }
  })
  split$genotype <- factor(split$genotype, levels = c("N2", "CB4856", "LSJ2", "AF16", "HK104"),
                           labels = c("N2-RIAILs", "CB-RIAILs", "LSJ2-RIAILs", "AF16-RIAILs", "HK104-RIAILs"))
  split <- split[!is.na(split$genotype),]
  test <- ggplot2::ggplot(split) + 
    ggplot2::geom_jitter(ggplot2::aes(x = genotype, y = pheno), alpha = 1, size = 0.5) + 
    ggplot2::geom_boxplot(ggplot2::aes(x = genotype, y = pheno, fill = genotype, alpha = 0.8), outlier.shape = NA) + 
    ggplot2::scale_fill_manual(values = c(`N2-RIAILs` = "orange", `CB-RIAILs` = "blue", LSJ2 = "green", AF16 = "indianred", HK104 = "gold")) + 
    ggplot2::facet_wrap(~marker, ncol = 5) + 
    ggplot2::theme_bw() + 
    ggplot2::theme(axis.text.x = ggplot2::element_text(size = textsize,face = "bold", color = "black"), 
                   axis.text.y = ggplot2::element_text(size = textsize, face = "bold", color = "black"), 
                   axis.title.x = ggplot2::element_text(size = titlesize, face = "bold", color = "black", vjust = -0.3), 
                   axis.title.y = ggplot2::element_text(size = titlesize, face = "bold", color = "black"), 
                   strip.text.x = ggplot2::element_text(size = titlesize, face = "bold", color = "black"), 
                   legend.position = "none", 
                   strip.background = ggplot2::element_rect(fill = "white", colour = "white"),
                   plot.margin = grid::unit(c(-0.5, 0.2, 0.2, 0.2), "cm"),
                   panel.background = ggplot2::element_rect(color = "black",size = 1.2)) + 
    ggplot2::labs(x = "", y = ylab, title = "")
  
  cowplot::ggdraw() +
    cowplot::draw_plot(test, 0, .04, 1, .96)
}
plot_add_int <- function(df) {
  ggplot2::ggplot(df) +
    ggplot2::geom_bar(data = df, ggplot2::aes(x = trait, y = VE, fill = factor(type, levels = c("Interactive", "Additive"))),
                      stat = "identity") +
    ggplot2::scale_fill_manual("Key", values = c("slateblue2", "cadetblue3"))+
    ggplot2::labs(y = "Variance Explained", x = "") + 
    ggplot2::geom_errorbar(ggplot2::aes(x = trait, ymin = lower, ymax = higher, group = n, linetype = type),
                           width = 0.7, position = position_dodge(0.4)) +
    ggplot2::theme(axis.text.x = ggplot2::element_blank(),
                   axis.text.y = ggplot2::element_text(size = textsize),
                   axis.ticks.x = ggplot2::element_blank(),
                   axis.title.x = ggplot2::element_text(size = titlesize, face = "bold"),
                   axis.title.y = ggplot2::element_text(size = titlesize, face = "bold"),
                   legend.position = "none")
}
getpheno <- function(nil, exp, cond, trt) {
  regressed <- allNILCSSregressed %>%
    dplyr::filter(condition == cond, trait == trt, experiment == exp, strain == nil)
  pheno <- abs(max(regressed$phenotype))
  range <- (max(regressed$phenotype)) + (min(regressed$phenotype))
  if(range < 65 && range > 5) { newpheno <- pheno + 7 } else { newpheno <- (pheno*1.4) } 
}
plotstats <- function(drug, trt, expr) {
  fullstats <- NULL
  for(j in 1:length(expr)) {
    e <- expr[j]
    stats <- css_nil_stats %>%
      dplyr::filter(exp == e, condition == drug, trait == trt)
    
    #make an empty dataframe
    statsdf <- setNames(data.frame(matrix(ncol = 4, nrow = 4)), c("strain", "significant", "pheno", "experiment"))
    statsdf$strain <- c("N2", "CB4856", stats$N2nil, stats$CBnil)
    statsdf$experiment <- c(e)
    
    sig <- 0.05
    
    parents <- if(stats$par_sig < 0.05) {parents <- TRUE} else {parents <- FALSE}
    nils <- if(stats$nils_sig< 0.05) {nils <- TRUE} else {nils <- FALSE}
    n2nilcb <- if(stats$N2nil_sig_CB< 0.05) {n2nilcb <- TRUE} else {n2nilcb <- FALSE}
    n2niln2 <- if(stats$N2nil_sig_N2< 0.05) {n2niln2 <- TRUE} else {n2niln2 <- FALSE}
    cbnilcb <- if(stats$CBnil_sig_CB< 0.05) {cbnilcb <- TRUE} else {cbnilcb <- FALSE}
    cbniln2 <- if(stats$CBnil_sig_N2< 0.05) {cbniln2 <- TRUE} else {cbniln2 <- FALSE}
    
    #If parents are sig
    if(parents==T) {
      #Check if nils are sig
      if(nils==T) {
        if(n2nilcb==F && cbniln2==F) {
          if(n2niln2==T && cbnilcb==T) {
            N2val <- "a"
            CBval <- "b"
            N2nilval <- "b"
            CBnilval <- "a"
          }
          if(n2niln2==T && cbnilcb==F) {
            N2val <- "a"
            CBval <- "bc"
            N2nilval <- "c"
            CBnilval <- "ab"
          }
          if(n2niln2==F && cbnilcb==T) {
            N2val <- "ab"
            CBval <- "c"
            N2nilval <- "ac"
            CBnilval <- "b"
          }
          if(n2niln2==F && cbnilcb==F) {
            N2val <- "ac"
            CBval <- "BD"
            N2nilval <- "ab"
            CBnilval <- "CD"
          }
        } else if(n2nilcb==T && cbniln2==T) {
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "c"
              CBnilval <- "d"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "c"
              CBnilval <- "b"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "a"
              CBnilval <- "c"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "a"
              CBnilval <- "b"
            }
        } else if(n2nilcb==T && cbniln2==F) {
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "c"
              CBnilval <- "a"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "c"
              CBnilval <- "ab"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "ab"
              CBval <- "c"
              N2nilval <- "a"
              CBnilval <- "b"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "ab"
              CBval <- "c"
              N2nilval <- "a"
              CBnilval <- "bc"
            }
        } else if(n2nilcb==F && cbniln2==T) { 
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "bc"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "ab"
              CBnilval <- "c"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "a"
              CBval <- "bc"
              N2nilval <- "ab"
              CBnilval <- "c"
            }
        }
          #nils not sig
      } else  {
          if(n2nilcb==F && cbniln2==F) {
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "bc"
              CBnilval <- "ac"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "b"
              CBnilval <- "ab"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "a"
              CBval <- "bc"
              N2nilval <- "ab"
              CBnilval <- "a"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "a"
              CBval <- "b"
              N2nilval <- "ab"
              CBnilval <- "ab"
            }
          } else if(n2nilcb==T && cbniln2==T) {
              if(n2niln2==T && cbnilcb==T) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "c"
                CBnilval <- "c"
              }
              if(n2niln2==T && cbnilcb==F) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "c"
                CBnilval <- "bc"
              }
              if(n2niln2==F && cbnilcb==T) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "ac"
                CBnilval <- "c"
              }
              if(n2niln2==F && cbnilcb==F) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "ac"
                CBnilval <- "bc"
              }
          } else if(n2nilcb==T && cbniln2==F) { 
              if(n2niln2==T && cbnilcb==T) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "c"
                CBnilval <- "ac"
              }
              if(n2niln2==T && cbnilcb==F) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "c"
                CBnilval <- "abc"
              }
              if(n2niln2==F && cbnilcb==T) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "a"
                CBnilval <- "a"
              }
              if(n2niln2==F && cbnilcb==F) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "a"
                CBnilval <- "ab"
              }
          } else if(n2nilcb==F && cbniln2==T) {
              if(n2niln2==T && cbnilcb==T) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "bc"
                CBnilval <- "c"
              }
              if(n2niln2==T && cbnilcb==F) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "b"
                CBnilval <- "b"
              }
              if(n2niln2==F && cbnilcb==T) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "abc"
                CBnilval <- "c"
              }
              if(n2niln2==F && cbnilcb==F) {
                N2val <- "a"
                CBval <- "b"
                N2nilval <- "ab"
                CBnilval <- "b"
              }
          }
        #parents are ns
    } 
      } else  {
      #check if nils are sig
      if(nils==T) {
        if(n2nilcb==F && cbniln2==F) {
          if(n2niln2==T && cbnilcb==T) {
            N2val <- "ab"
            CBval <- "ac"
            N2nilval <- "c"
            CBnilval <- "b"
          }
          if(n2niln2==T && cbnilcb==F) {
            N2val <- "a"
            CBval <- "ab"
            N2nilval <- "b"
            CBnilval <- "a"
          }
          if(n2niln2==F && cbnilcb==T) {
            N2val <- "ab"
            CBval <- "a"
            N2nilval <- "a"
            CBnilval <- "b"
          }
          if(n2niln2==F && cbnilcb==F) {
            N2val <- "ab"
            CBval <- "ab"
            N2nilval <- "a"
            CBnilval <- "b"
          }
        } else if(n2nilcb==T && cbniln2==T) {
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "a"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "ab"
              N2nilval <- "c"
              CBnilval <- "b"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "ab"
              CBval <- "a"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "ab"
              CBval <- "ac"
              N2nilval <- "b"
              CBnilval <- "c"
            }
        } else if(n2nilcb==T && cbniln2==F) {
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "ab"
              CBval <- "a"
              N2nilval <- "c"
              CBnilval <- "b"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "a"
              N2nilval <- "b"
              CBnilval <- "a"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "abc"
              CBval <- "a"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "ab"
              CBval <- "a"
              N2nilval <- "b"
              CBnilval <- "a"
            }
        } else if(n2nilcb==F && cbniln2==T) {
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "ab"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "abc"
              N2nilval <- "b"
              CBnilval <- "c"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "a"
              CBval <- "a"
              N2nilval <- "a"
              CBnilval <- "b"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "a"
              CBval <- "ab"
              N2nilval <- "a"
              CBnilval <- "b"
            }
        }
          #nils not sig 
      } else {
          if(n2nilcb==F && cbniln2==F) {
            #START HERE
            if(n2niln2==T && cbnilcb==T) {
              N2val <- "a"
              CBval <- "ab"
              N2nilval <- "bc"
              CBnilval <- "ac"
            }
            if(n2niln2==T && cbnilcb==F) {
              N2val <- "a"
              CBval <- "ab"
              N2nilval <- "b"
              CBnilval <- "ab"
            }
            if(n2niln2==F && cbnilcb==T) {
              N2val <- "ab"
              CBval <- "a"
              N2nilval <- "ac"
              CBnilval <- "bc"
            }
            if(n2niln2==F && cbnilcb==F) {
              N2val <- "a"
              CBval <- "a"
              N2nilval <- "a"
              CBnilval <- "a"
            }
          } else if(n2nilcb==T && cbniln2==T) {
              if(n2niln2==T && cbnilcb==T) {
                N2val <- "a"
                CBval <- "ab"
                N2nilval <- "c"
                CBnilval <- "bc"
              }
              if(n2niln2==T && cbnilcb==F) {
                N2val <- "a"
                CBval <- "ab"
                N2nilval <- "c"
                CBnilval <- "bc"
              }
              if(n2niln2==F && cbnilcb==T) {
                N2val <- "ab"
                CBval <- "a"
                N2nilval <- "bc"
                CBnilval <- "c"
              }
              if(n2niln2==F && cbnilcb==F) {
                N2val <- "ab"
                CBval <- "ac"
                N2nilval <- "BD"
                CBnilval <- "CD"
              }
          } else if(n2nilcb==T && cbniln2==F) {
              if(n2niln2==T && cbnilcb==T) {
                N2val <- "ab"
                CBval <- "a"
                N2nilval <- "c"
                CBnilval <- "bc"
              }
              if(n2niln2==T && cbnilcb==F) {
                N2val <- "a"
                CBval <- "a"
                N2nilval <- "b"
                CBnilval <- "ab"
              }
              if(n2niln2==F && cbnilcb==T) {
                N2val <- "ab"
                CBval <- "a"
                N2nilval <- "b"
                CBnilval <- "b"
              }
              if(n2niln2==F && cbnilcb==F) {
                N2val <- "ab"
                CBval <- "a"
                N2nilval <- "b"
                CBnilval <- "ab"
              }
          } else if(n2nilcb==F && cbniln2==T) {
              if(n2niln2==T && cbnilcb==T) {
                N2val <- "a"
                CBval <- "ab"
                N2nilval <- "bc"
                CBnilval <- "c"
              }
              if(n2niln2==T && cbnilcb==F) {
                N2val <- "a"
                CBval <- "ab"
                N2nilval <- "b"
                CBnilval <- "b"
              }
              if(n2niln2==F && cbnilcb==T) {
                N2val <- "a"
                CBval <- "a"
                N2nilval <- "ab"
                CBnilval <- "b"
              }
              if(n2niln2==F && cbnilcb==F) {
                N2val <- "a"
                CBval <- "ab"
                N2nilval <- "ac"
                CBnilval <- "bc"
              }
          }
      }
    }
    statsdf$significant <- c(N2val, CBval, N2nilval, CBnilval)
    statsdf$pheno <- sapply(statsdf$strain, function(x) getpheno(x, e, drug, trt))
    #Bind stats dataframes
    fullstats <- rbind(fullstats, statsdf)
  }
  return(fullstats)
}

splitmap <- allAnnotatedLods %>%
  dplyr::mutate(condition = stringr::str_split_fixed(trait, "\\.", 2)[,1]) %>%
  dplyr::mutate(trait = stringr::str_split_fixed(trait, "\\.", 2)[,2]) %>%
  dplyr::filter(!grepl("red|yellow|green|f.|iqr", trait)) %>%
  dplyr::arrange(condition, trait)


```

```{r s2_2,fig.width=7.5, fig.height=3,warning=F, message=F, echo=F,comment="K",results='asis', dpi = 300}

# abbreviate category names for plotting
plotcat <- assays_category %>%
    dplyr::mutate(primary_category = ifelse(primary_category == "recapitulation", "Recapitulation",
                                            ifelse(primary_category == "no_qtl_effect", "No effect",
                                                   ifelse(primary_category == "unidirectional_transgressive", "Unidirectional",
                                                          ifelse(primary_category == "bidirectional_transgressive", "Bidirectional",
                                                                 ifelse(primary_category == "miscellaneous", "Miscellaneous",
                                                                        ifelse(primary_category == "parents_not_significant", "No parental diff.", NA)))))))

for(drug in unique(splitmap$condition)) {
 drugmap <- splitmap %>%
    dplyr::filter(condition == drug) %>%
    na.omit() %>%
    dplyr::distinct(chr, trait, .keep_all = TRUE)
  
  for(trt in unique(drugmap$trait)) {
    traitmap <- drugmap %>% 
      dplyr::filter(trait == trt) %>%
      dplyr::arrange(chr, pos)
   
    #Mapping
    lod <- maxlodplot_kt(splitmap %>% dplyr::filter(condition == drug, trait == trt))
    VE <- plot_add_int(VE_SE_QTL %>% dplyr::filter(condition == drug, trait == trt))
    print(cowplot::plot_grid(lod, VE, nrow = 1, ncol = 2, rel_widths = c(5, 1), labels = c("A", "B")))
    
    #CSS and NILs if applicable
    count <- 0
    blankplot <-  ggplot2::ggplot() + theme_bw() + theme(rect = element_blank())
    for(i in 1:nrow(traitmap)) {
      test <- traitmap[i,]
      rilnil_IVL <- NULL
      rilnil_IVR <- NULL
      rilnil_V <- NULL
      css <- ggplot2::ggplot() + ggplot2::geom_blank() + theme(rect = element_blank())
      nil <- ggplot2::ggplot() + ggplot2::geom_blank() + theme(rect = element_blank())
      # make ril and NIL (maybe) if in IVL hotspot
      if(test$chr == "IV" && test$ci_l_pos <= 9334865 && test$ci_r_pos >= 3684741) {
          if(count < 1) { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                              dplyr::filter(chr == "IV", ci_l_pos <= 9334865, ci_r_pos >= 3684741) %>% 
                              dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c("C")) }
        else { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                              dplyr::filter(chr == "IV", ci_l_pos <= 9334865, ci_r_pos >= 3684741) %>% 
                              dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c(" ")) }
        if(drug %in% unique(chrIVLregressed$condition)) { #IVL hotspot
            # get category of nil/css trait to add to figure title
            nil_cat <- plotcat %>%
                dplyr::filter(condition == drug, trait == trt, exp == "IVL") %>%
                dplyr::pull(primary_category)
          nil <- quick_plot_IVL(drug, trt, plotstats(drug, trt, "IVL"), t = paste("NIL -", nil_cat))
        } 
          rilnil_IVL <- cowplot::plot_grid(ril, nil, css, nrow = 1, ncol = 3, rel_widths = c(0.8, 1, 1))
      } else      
        # make ril and NIL (maybe) if in IVR hotspot
      if(test$chr == "IV" && test$ci_l_pos <= 17493829 && test$ci_r_pos >= 12865211) {
        if(count < 1) { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                            dplyr::filter(chr == "IV", ci_l_pos <= 17493829, ci_r_pos >= 12865211) %>%
                            dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c("C")) }
        else { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                            dplyr::filter(chr == "IV", ci_l_pos <= 17493829, ci_r_pos >= 12865211) %>%
                            dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c(" ")) }
        if(drug %in% unique(chrIVRregressed$condition)) { #IVR hotspot
            # get category of nil/css trait to add to figure title
            nil_cat <- plotcat %>%
                dplyr::filter(condition == drug, trait == trt, exp == "IVR") %>%
                dplyr::pull(primary_category)
          nil <- quick_plot_IVR(drug, trt, plotstats(drug, trt, "IVR"), t = paste("NIL -", nil_cat))
        } 
          rilnil_IVR <- cowplot::plot_grid(ril, nil, css, nrow = 1, ncol = 3, rel_widths = c(0.8, 1, 1))
      } else
              # make ril and NIL (maybe) if in V hotspot
      if(test$chr == "V" && test$ci_l_pos <= 13839858 && test$ci_r_pos >= 7082839) {
        if(count < 1) { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                            dplyr::filter(chr == "V", ci_l_pos <= 13839858, ci_r_pos >= 7082839) %>% 
                            dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c("C")) }
        else { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                            dplyr::filter(chr == "V", ci_l_pos <= 13839858, ci_r_pos >= 7082839) %>% 
                            dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c(" "))  }
        if(drug %in% unique(chrVregressed$condition)) { #V hotspot
            # get category of nil/css trait to add to figure title
            css_cat <- plotcat %>%
                dplyr::filter(condition == drug, trait == trt, exp == "CSSV") %>%
                dplyr::pull(primary_category)
            nil_cat <- plotcat %>%
                dplyr::filter(condition == drug, trait == trt, exp == "V") %>%
                dplyr::pull(primary_category)
            css <- quick_plot_cssV(drug, trt, plotstats(drug, trt, "CSSV"), t = paste("CSS -", css_cat))
            nil <- quick_plot_V(drug, trt, plotstats(drug, trt, "V"), t = paste("NIL - ", nil_cat))
        } 
        rilnil_V <- cowplot::plot_grid(ril, nil, css, nrow = 1, ncol = 3, rel_widths = c(0.8, 1, 1))
      } else {
          # make RIL plot if not in a hotspot
          if(count < 1) { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                              dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c("C")) }
        else { ril <- cowplot::plot_grid(pxgplot_kt(phenocross, test %>% 
                              dplyr::mutate(trait = paste0(condition, ".", trait)), ylab = test$trait), labels = c(" ")) }
      }
      
    #Print all the plots
    if(is.null(rilnil_IVL) && is.null(rilnil_IVR) && is.null(rilnil_V)) {
      print(cowplot::plot_grid(ril, blankplot, blankplot, nrow = 1, ncol = 3, rel_widths = c(0.8, 1, 1)))
    } else
    if(!is.null(rilnil_IVL)) {
      print(rilnil_IVL)
    } else
    if(!is.null(rilnil_IVR)) {
      print(rilnil_IVR)
    } else
    if(!is.null(rilnil_V)) {
      print(rilnil_V)
    }
    count <- count + 1
    cat("\n\n\n")
    }
    cat("\n\n\n")
    cat("\n\n\\pagebreak\n")
  }
}


```

**Figure S2** QTL linkage mapping, NIL and CSS results, and variance component contributions. (**A**) The maximum LOD score (y-axis) for each marker across the genome (x-axis), split by chromosome, is plotted as a black line. Significant QTL are indicated by a red triangle at the marker with the maximum LOD score and a light blue ribbon spanning the 95% confidence interval. The estimated phenotypic variation in the RIAILs explained by each QTL is indicated above each peak. (**B**) The proportion of phenotypic variation across the RIAILs caused by additive (light blue) and interactive (dark blue) genetic components are indicated. Solid and dashed error bars show the standard error around additive and interactive component estimates, respectively. (**C**) For each QTL plotted in A, the residual phenotypes (y-axis) of RIAILs split by genotype at the marker with the maximum LOD score (x-axis) are plotted as Tukey box plots. Data from RIAILs with the N2 or the CB4856 allele at the QTL peak marker are colored in orange and blue, respectively. For traits in which NILs and CSSs were assayed, the residual phenotypic values (y-axis) of N2, CB4856, and reciprocal introgressed NILs or CSSs are plotted as Tukey box plots. Different letters represent significant differences (p<0.05) between strains (TukeyHSD). The genotype of each strain on the x-axis is modeled by the colored rectangles beneath the plots (N2 genotypes are orange, CB4856 genotypes are blue). The category assigned to each assay is marked above each NIL/CSS phenotype plot.


```{r s3,warning=F, message=F, echo=F,comment="K",results='asis',fig.width=7.5, fig.height=8.85}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(cowplot)
library(Hmisc)
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS4_allAnnotatedLods.Rda?raw=TRUE")
# source_data("https://github.com/AndersenLab/QTLhotspot/blob/master/data/FileS5_varianceComponents.Rda?raw=TRUE")

peaks <- allAnnotatedLods %>%
    na.omit()

VE <- varianceComponents %>%
  dplyr::select(condition, trait, narrowsense_h2, interaction_VE) %>%
  tidyr::gather(type, VE, narrowsense_h2:interaction_VE) %>%
  dplyr::mutate(type = ifelse(type == "narrowsense_h2", "Additive", "Interactive"))
  
SE <- varianceComponents %>%
  dplyr::select(condition, trait, narrowsense_h2_SE, interaction_SE) %>%
  tidyr::gather(type, SE, narrowsense_h2_SE:interaction_SE) %>%
  dplyr::mutate(type = ifelse(type == "narrowsense_h2_SE", "Additive", "Interactive"))

VE_SE_QTL <- dplyr::left_join(VE, SE) %>%
  dplyr::mutate(n = 1:nrow(.))

VE_SE_QTL$type <- factor(VE_SE_QTL$type, levels = c("Interactive", "Additive"))
VE_SE_QTL <- VE_SE_QTL %>%
  mutate(lower = VE - SE, higher = VE + SE)

VE_SE_QTL$lower[VE_SE_QTL$type == "Interactive"] <- with(VE_SE_QTL,VE[type == "Additive"] - SE[type == "Interactive"] + VE[type == "Interactive"])
VE_SE_QTL$higher[VE_SE_QTL$type == "Interactive"] <- with(VE_SE_QTL,VE[type == "Interactive"] + VE[type == "Additive"] + SE[type == "Interactive"])

for(i in 1:nrow(VE_SE_QTL)) {
  if(VE_SE_QTL$lower[i] < 0) {
    VE_SE_QTL$lower[i] <- 0
  }
}

textsize <- 8
titlesize <- 10

VE_SE_QTL <- VE_SE_QTL %>%
  dplyr::mutate(condtrt = paste0(condition, ".", trait)) %>%
  dplyr::filter(condtrt %in% unique(peaks$trait)) %>%
  dplyr::arrange(condition, trait) %>%
  dplyr::mutate(condition = Hmisc::capitalize(condition))

allinteractions <- ggplot2::ggplot(VE_SE_QTL) +
  ggplot2::geom_bar(data = VE_SE_QTL,ggplot2:: aes(x = trait, 
                                 y = VE, fill = factor(type, levels = c("Interactive", "Additive"))), stat = "identity") +
  ggplot2::scale_fill_manual("Key", values = c("slateblue2", "cadetblue3"))+
  ggplot2::coord_flip() +
  ggplot2::facet_grid(~condition, scales = "free_y", switch = "both") +
  ggplot2::labs(y = "Variance Explained", x = "") + 
  ggplot2::geom_errorbar(ggplot2::aes(x = trait, ymin = lower, ymax = higher, group = n, linetype = type), width = 0.7, position = position_dodge(0.4)) +
  ggplot2::theme(legend.position = "none",
        strip.background = ggplot2::element_rect(colour = "black", fill = "white", linetype = "solid", size = 1),
        strip.text = ggplot2::element_text(size = titlesize, face = "bold"),
        strip.text.x = ggplot2::element_text(margin = margin(4, 0, 4, 0)),
        axis.text.x = ggplot2::element_text(size = textsize),
        axis.text.y = ggplot2::element_text(size = textsize),
        axis.title.x = ggplot2::element_blank()) +
  ggplot2::facet_wrap(~condition, scales = "free", ncol = 3, nrow = 6)

legstartx <- 0.5 #position where the top left corner of the legend begins
legstarty <- 0.1 #position where the top left corner of the legend begins
width <- 0.02 #width of the boxes/lines of legend
sp <- 0.01 #spacing within legend

plot <- cowplot::ggdraw() +
  cowplot::draw_plot(allinteractions, 0, 0, 1, 1) +
  ggplot2::geom_rect(ggplot2::aes(xmin = legstartx - sp, xmax = legstartx + width*12+sp*2, 
                                  ymin = legstarty-width-sp, ymax = legstarty + sp), colour = "black", fill = "white") +
  ggplot2::geom_rect(ggplot2::aes(xmin = legstartx, xmax = legstartx + width, ymax = legstarty, ymin = legstarty - width*0.8), 
                     colour = "black", fill = "cadetblue3") +
  cowplot::draw_label("Additive", x = legstartx + width*3 + sp, y = legstarty - width*0.35, size = titlesize, fontface = "bold") +
  ggplot2::geom_segment(ggplot2::aes(x = legstartx - width*.25, xend = legstartx + width*1.35, 
                                     y = legstarty - width*.35, yend = legstarty - width*.35), colour = "black", linetype = "solid")+ 
  ggplot2::geom_rect(ggplot2::aes(xmin = legstartx+width*6, xmax = legstartx + width*7, ymax = legstarty, 
                                  ymin = legstarty - width*0.8), colour = "black", fill = "slateblue2") +
  cowplot::draw_label("Interactive", x = legstartx + width*9.5 + sp, y = legstarty - width*0.35, size = titlesize, fontface = "bold") +
  ggplot2::geom_segment(ggplot2::aes(x = legstartx+width*5.75, xend = legstartx + width*7.5, 
                                     y = legstarty - width*.35, yend = legstarty - width*.35), colour = "black", linetype = "dashed") 

print(plot)

```

**Figure S3** Additive and interactive genetic components. The proportion of phenotypic variation predicted to be caused by additive and interactive genetic components is shown for each of the 47 traits that represent one of the 82 QTL identified by linkage mapping. For each toxin, the fraction of phenotypic variation (x-axis) in a given trait (y-axis) that is attributable to additive (light blue) versus interactive (dark blue) genetic components is shown as a stacked bar plot. Solid and dashed error bars show the standard error around the mean of additive and interactive components, respectively.


```{r s4, echo=FALSE, out.width='100%'}
figS5_path <- "https://cdn.rawgit.com/AndersenLab/QTLhotspot/ed981acd/figures/extra/figS5_categorization2.pdf"
download.file(figS5_path, destfile = "~/Downloads/figS5.pdf")
knitr::include_graphics("~/Downloads/figS5.pdf")

```

**Figure S4** NIL and CSS trait categorizations. (**A**) Flowchart for categorizing traits from the NIL or CSS phenotyping assays. (**B**) Six categories across both NIL and CSS assays for traits on chromosome V. The miscellaneous category is not depicted, but encompasses any other combination of NIL and CSS assay results.
